### 2024-02-27 manuscript.tex
Addressed reviewer comments about overstating the conclusions and minimizing caveats

Therefore, in this work we applied a series of phylogenetic models to dissect of evolution of a set of orthologous IDRs identified in the \textit{Drosophila} genome. Our analyses span multiple levels, ranging from the sequences that compose these regions to the distributed features that characterize them as a whole. For the latter, though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, we instead leveraged a fully statistical phylogenetic comparative framework~\cite{Cornwell2017}. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint on features independent of any assumptions about the underlying process of sequence evolution. However, we also propose hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. We found that IDRs exhibit unique patterns of amino acid substitution and that in some proteins disorder itself is a dynamically evolving property. Furthermore, though IDRs are broadly unconstrained along several axes of feature evolution, we identified signals of widespread constraint in IDRs, indicating conservation of distributed features is mechanism of IDR evolution common to multiple biological systems. Unlike in yeast, however, we observed limited evidence of IDR clusters with specific biological functions, which suggests a more complex relationship between evolutionary constraints and function in the IDRs of multicellular organisms.

@@

To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig~\ref{fig:substitution}, beginning with the frequency vectors. The disorder regions show an enrichment of ``disorder-promoting'' residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig~\ref{fig:substitution}A). The exchangeability matrices fit to the disorder and order regions have similar overall patterns of high and low coefficients (Fig~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear differences within and between the disorder-enriched and -depleted residues. The disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig~\ref{fig:substitution}D). Likewise, we observe a trend in the log ratios of the rate coefficients where the coefficients above the diagonal are generally positive, and those below the diagonal are generally negative (Fig~\ref{fig:substitution}E-F). As the coefficients model the one-way rates of substitution between residues with the vertical and horizontal axes indicating the initial and target residues, respectively, this suggests a net flux towards a more disorder-like composition. However, the coefficients between the disorder-depleted and -enriched classes of residues for both the exchangeability and rate matrices should be interpreted with caution, as they are estimated with a high amount of uncertainty (\ref{sfig:CV_ematrix}-\ref{sfig:CV_rmatrix}~Fig).

>>>>

Therefore, in this work we applied a series of phylogenetic models to dissect of evolution of a set of orthologous IDRs identified in the \textit{Drosophila} genome. Our analyses span multiple levels, ranging from the sequences that compose these regions to the distributed features that characterize them as a whole. For the latter, though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, we instead leveraged a fully statistical phylogenetic comparative framework~\cite{Cornwell2017}. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint on features independent of any assumptions about the underlying process of sequence evolution. However, we also propose hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. We found that IDRs exhibit unique patterns of amino acid substitution and that in some proteins disorder itself is a dynamically evolving property. Furthermore, though IDRs are broadly unconstrained along several axes of feature evolution, we identified signals of widespread constraint in IDRs, indicating conservation of distributed features is mechanism of IDR evolution common to multiple biological systems. Unlike in yeast, though, we observed limited evidence of IDR clusters with specific biological functions, which suggests a more complex relationship between evolutionary constraints and function in the IDRs of multicellular organisms. These conclusions, however, are tempered by several methodological limitations, \textit{e.g.}, the application of continuous models of trait evolution to discrete data, which are explored in greater detail in the discussion.

@@

To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig~\ref{fig:substitution}, beginning with the frequency vectors. The disorder regions show an enrichment of ``disorder-promoting'' residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig~\ref{fig:substitution}A). The exchangeability matrices fit to the disorder and order regions have similar overall patterns of high and low coefficients (Fig~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear differences within and between the disorder-enriched and -depleted residues. The disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig~\ref{fig:substitution}D). Likewise, we observe a trend in the log ratios of the rate coefficients where the coefficients above the diagonal are generally positive, and those below the diagonal are generally negative (Fig~\ref{fig:substitution}E-F). As the coefficients model the one-way rates of substitution between residues with the vertical and horizontal axes indicating the initial and target residues, respectively, this suggests a net flux towards a more disorder-like composition. Though, the coefficients between the disorder-depleted and -enriched classes of residues for both the exchangeability and rate matrices should be interpreted with caution, as they are estimated with a high amount of uncertainty (\ref{sfig:CV_ematrix}-\ref{sfig:CV_rmatrix}~Fig). A second, more general, caveat is these trends may result from fitting substitution matrices to alignments which were created using other substitution matrices derived from alignments of largely structured proteins. However, as addressed in the discussion, their consistency with several similar analyses suggests they represent true differences in the substitution patterns of IDRs~\cite{Brown2009, Szalkowski2011}.
